Near Optimal Behavior via Approximate State Abstraction

### 2016-02-05 paper/results_discussion.tex
added new visuals

\subfigure[NChain]{
\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
}
\subfigure[Minefield]{
\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
}
\subfigure[Taxi]{
\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
}
\subfigure[Random]{
\includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
}
\caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value\label{fig:main_empirical_results1}}
\end{figure*}

>>>>

\subfigure[NChain]{
\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy.pdf}
}
\subfigure[Minefield]{
\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy.pdf}
}
\subfigure[Taxi]{
\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy.pdf}
}
\subfigure[Random]{
\includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy.pdf}
}
\caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value\label{fig:main_empirical_results1}}
\end{figure*}
